Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-08-22 manuscript.tex
Will separate the division scheme in methods

We have developed a modified version
of the recursive scheme of \citet{Li2011}.
We fix the number of nodes in the GLQ
$N^\lambda=N^\phi=N^r=2$
so that the distance between nodes
in the radial, longitudinal, and latitudinal directions
are approximately the dimensions of the tesseroid.
We define the distance $d$ as
the Cartesian distance between
the computation point $P$
and the center of the top face of the tesseroid
(Fig.~\ref{fig:ratio}a).
Thus, the rule-of-thumb of \citet{Ku1977}
can be written as

\begin{equation}
    \frac{d}{L} < r,
    \label{eq:ratio}
\end{equation}

\noindent
where
$L$ is one of the dimensions of the tesseroid
and
$r$ is the distance/size ratio.
For \citet{Ku1977} this ratio should be equal to one.
The dimensions of the tesseroid are

@@

\subsection{Comparison with a spherical half-shell}

>>>>

THE EFFECTS OF THE NUMBER OF NODES AND DISTANCE ON THE COMPUTATIONS.

\subsection{Recursive division algorithm}

We have developed a modified version
of the recursive division scheme of \citet{Li2011}.
We fix the number of nodes in the GLQ
$N^\lambda=N^\phi=N^r=2$
so that the distance between nodes
in the radial, longitudinal, and latitudinal directions
are approximately the dimensions of the tesseroid
\citep{Wild-Pfeiffer2008}.
We define the distance $d$ as
the Cartesian distance between
the computation point $P$
and the center of the top face of the tesseroid
(Fig.~\ref{fig:ratio}a).

DESCRIBE ALGORITHM FIRST.

Thus, the rule-of-thumb of \citet{Ku1977}
can be interpreted as

\begin{equation}
    \frac{d}{L_\zeta} < r,
    \label{eq:ratio}
\end{equation}

\noindent
where
$L_\zeta$, $\zeta \in \{r, \phi, \lambda\}$,
is one of the dimensions of the tesseroid
and
$r$ is the maximum allowed ratio between distance and size.
For \citet{Ku1977}, this ratio should be equal to one.
The dimensions of the tesseroid are

@@

\subsection{Determination of $r$ by comparison with a spherical shell}
